Determining what makes some TADs unpredictable

### 2019-04-16 Scripts/evaluating_variable_importances.Rmd
editted results scripts

rankdata <- cbind(vim.K562.smote.ranks$Rank.10kb,
                  vim.K562.smote.ranks$Rank.25kb,
				  vim.K562.smote.ranks$Rank.50kb,
				  vim.K562.smote.ranks$Rank.100kb)
rownames(rankdata) <- vim.K562.smote.ranks$Feature
colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")

>>>>

rankdata <- cbind(vim.K562.smote.ranks$Rank.10kb,
                  vim.K562.smote.ranks$Rank.25kb,
				  vim.K562.smote.ranks$Rank.50kb,
				  vim.K562.smote.ranks$Rank.100kb)
rownames(rankdata) <- vim.K562.smote.ranks$Feature
colnames(rankdata) <- c("10 kb", "25 kb", "50 kb", "100 kb")
rankdata <- rankdata[order(rankdata[,1], decreasing = FALSE),]
rankdata <- rankdata[1:20,]

### 2019-04-16 Scripts/investigating_misclassified_TADs.Rmd
editted results scripts

```{r}
#reading in test data and reducing
test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
names(test) <- gsub(paste(c("`", 
                            "Gm12878", 
                            "-", 
                            #"_", 
                            #"dist", "count", "perc",
                            "Haib", 
                            "Sydh",
                            "Uta",
                            "Uw",
                            "Broad",
                            "Uchicago"), collapse = "|"), "", names(test))
enetcoefs <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
test <- test[,c(1,which(names(test) %in% enetcoefs))]

>>>>

```{r}
#reading in test data and reducing
test <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/test.rds")
names(test) <- gsub(paste(c("`", 
                            "Gm12878", 
                            "-", 
                            #"_", 
                            #"dist", "count", "perc",
                            "Haib", 
                            "Sydh",
                            "Uta",
                            "Uw",
                            "Broad",
                            "Uchicago"), collapse = "|"), "", names(test))
enetcoefs <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/enetcoefs.rds")
test <- test[,c(1,which(names(test) %in% enetcoefs))]
